Location of Shrimp Farms

### 2021-02-17 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
added and fixed subregions. Fixed some other classifications too

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                        area_ha = c(1516, 459, 26762, 6388)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

guana_punta <- provinces  %>%
  dplyr::filter(NAME_1 %in% c("Guanacaste", "Puntarenas"))

mapview(guana_punta)

# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)

# world <- st_as_sf(world)

costa_world_crs <- st_transform(guana_punta, crs(coast_raw))

costa_world_crop <- st_crop(coast_raw, costa_world_crs) %>% ## crop to costa rica extent 
  filter(FID %in% c(245909:245926)) %>% ## filter for the correct coastline 
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(costa_world_crop)

c_meters <- st_transform(costa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(c_meters)

buff <- st_buffer(c_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(costa_world_crop))
mapview(buffer_outline_fixed)

@@

costa_crop <- as(linestring_fix, "Spatial")
mapview(costa_crop)

costa_points_lines <- sample.line(costa_crop, n = 106) ## equally place the number of farms along the coastline

costa_points <- st_as_sf(costa_points_lines) %>%
  mutate(new_id = 1:318) %>%
  filter(new_id %in% c(1:88, 105:106))
mapview(costa_points)

cri_pts <- st_centroid(costa_points)

cri_pts_latlon <- st_transform(cri_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_cri <- data.frame(do.call(rbind, st_geometry(cri_pts_latlon)))
names(farms_cri) <- c("lon", "lat")

farms_cri_final <- farms_cri %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

## visualize it 
farms_cri <-  st_as_sf(farms_cri, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50)) %>%
  mutate(iso3c = "SLV") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018046544221823, 5.674088, 4.984545, 5.597252273526056, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.43838831493285, 102.721589, 103.328932, 102.82739417198427, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

# philly_world_crop <- philly_world_crop %>%
#   mutate(new_id = 1) %>%
#   group_by(new_id) %>%
#   summarise(geometry = st_union(geometry)) %>%
#   ungroup()
# 
# mapview(philly_world_crop)
# 
# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters
# mapview(p_meters)
# 
# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
# mapview(buff)
# 
# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline
# mapview(linestring)
# 
# ## now reproject back to original
# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
# mapview(buffer_outline_fixed)
# 
# 
# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
# mapview(philly2)
# 
# p_meters2 <- st_transform(philly2, crs = 7801) ## transform to a crs that can buffer in meters
# mapview(p_meters2)
# 
# buff2 <- st_buffer(p_meters2, dist = 9000)
# mapview(buff2)
# intersection_fixed <- st_transform(buff2, crs = crs(philly_world_crop))
# mapview(intersection_fixed)
# 
# linestring_fix <- st_difference(buffer_outline_fixed, intersection_fixed) ## now grab only the outline
# mapview(linestring_fix)

@@

## Start with Batticaloa
# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)

# world <- st_as_sf(world)

@@

farms_bat_lka_final <- farms_bat_lka %>%
  mutate(area_ha = 2.583333)

@@

## Now do puttalam
# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)
# 
# world <- st_as_sf(world)

puttalam_world_crs <- st_transform(puttalam_shp, crs(coast_raw))

@@

puttalam_points_lines <- sample.line(puttalam_crop, n = 1361) ## equally place the number of farms along the coastline 
class(puttalam_points_lines)
plot(puttalam_points_lines)

puttalam_points <- st_as_sf(puttalam_points_lines) %>%
  mutate(new_id = 1:1361) %>%
  filter(new_id %in% c(230:1360, 1:194, 199:217))
mapview(puttalam_points)

@@

farms_put_lka_final <- farms_put_lka %>%
  mutate(area_ha = 3.348214)

>>>>

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200),
                        subregion = c("Pará", "Maranhão", "Piauí", "Ceará", "Rio Grande do Norte", "Paraíba", "Pernambuco", "Alagoas", "Sergipe", "Bahia", "Paraná", "Santa Catarina")) %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                        area_ha = c(1516, 459, 26762, 6388), subregion = c("Kampot", "Kep", "Koh Kong", "Preah Sihanouk")) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

guana <- provinces  %>%
  dplyr::filter(NAME_1 %in% c("Guanacaste"))

punta <- provinces  %>%
  dplyr::filter(NAME_1 %in% c("Puntarenas"))

mapview(guana)
mapview(punta)

## First do Guanacaste
guana_world_crs <- st_transform(guana, crs(coast_raw))

guana_world_crop <- st_crop(coast_raw, guana_world_crs) %>% ## crop to costa rica extent 
  filter(FID %in% c(245921:245926)) %>% ## filter for the correct coastline 
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(guana_world_crop)

g_meters <- st_transform(guana_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(g_meters)

buff <- st_buffer(g_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(guana_world_crop))
mapview(buffer_outline_fixed)

@@

guana_crop <- as(linestring_fix, "Spatial")
mapview(guana_crop)

guana_points_lines <- sample.line(guana_crop, n = 55) ## equally place the number of farms along the coastline

guana_points <- st_as_sf(guana_points_lines) %>%
  mutate(new_id = 1:55) %>%
  filter(new_id %in% c(5:49))
mapview(guana_points)

guana_pts <- st_centroid(guana_points)

guana_pts_latlon <- st_transform(guana_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_guana <- data.frame(do.call(rbind, st_geometry(guana_pts_latlon)))
names(farms_guana) <- c("lon", "lat")

farms_guana_final <- farms_guana %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially") %>%
  mutate(subregion = "Guanacaste")

## Now do puntarenas
punta_world_crs <- st_transform(punta, crs(coast_raw))

punta_world_crop <- st_crop(coast_raw, punta_world_crs) %>% ## crop to costa rica extent 
  filter(FID %in% c(245909:245917, 245919:245920)) %>% ## filter for the correct coastline 
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(punta_world_crop)

p_meters <- st_transform(punta_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(p_meters)

buff <- st_buffer(p_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(punta_world_crop))
mapview(buffer_outline_fixed)

buffer_outlined_fixed2 <- buffer_outline_fixed[1, ]
mapview(buffer_outlined_fixed2)

linestring_fix <- st_difference(buffer_outlined_fixed2, costa_rica) ## now grab only the outline 
mapview(linestring_fix)

punta_crop <- as(linestring_fix, "Spatial")
mapview(punta_crop)

punta_points_lines <- sample.line(punta_crop, n = 60) ## equally place the number of farms along the coastline

punta_points <- st_as_sf(punta_points_lines) %>%
  mutate(new_id = 1:60) %>%
  filter(new_id %in% c(2:46))
mapview(punta_points)

punta_pts <- st_centroid(punta_points)

punta_pts_latlon <- st_transform(punta_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_punta <- data.frame(do.call(rbind, st_geometry(punta_pts_latlon)))
names(farms_punta) <- c("lon", "lat")

farms_punta_final <- farms_punta %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially") %>%
  mutate(subregion = "Puntarenas")

farms_cri_final <- rbind(farms_punta_final, farms_guana_final)

## visualize it 
farms_cri <-  st_as_sf(farms_cri_final, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50),
                        subregion = c("La Paz", "La Unión")) %>%
  mutate(iso3c = "SLV") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018046544221823, 5.674088, 4.984545, 5.597252273526056, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.43838831493285, 102.721589, 103.328932, 102.82739417198427, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area,
                        subregion = c("Ayer Hangat, Kedah", "Sebatu, Malacca", "Kuching, Sarawak", "Pekan, Pahang", "Setiu, Terengganu", "Marang, Terengganu", "Setiu, Terengganu", "Tanjung Manis, Sarawak", "Rungkup, Perak", "Sabak, Selangor", "Pekan, Pahang")) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA ), 
                        subregion = c("Rahkine", "Ayeyarwaddy", "Yangon", "Mon", "Thaninthary")) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

@@

## Start with Batticaloa

@@

farms_bat_lka_final <- farms_bat_lka %>%
  mutate(area_ha = 2.583333) %>%
  mutate(subregion = "Batticaloa")

@@

## Now do puttalam
puttalam_world_crs <- st_transform(puttalam_shp, crs(coast_raw))

@@

puttalam_points_lines <- sample.line(puttalam_crop, n = 1800) ## equally place the number of farms along the coastline

puttalam_points <- st_as_sf(puttalam_points_lines) %>%
  mutate(new_id = 1:1800) %>%
  filter(new_id %in% c(457:1800))
mapview(puttalam_points)

@@

farms_put_lka_final <- farms_put_lka %>%
  mutate(area_ha = 3.348214)  %>%
  mutate(subregion = "Puttalam")
